
\documentclass{tufte-handout}
\input{checklist-header}


\begin{document}
\thispagestyle{firstpage}
    \begin{fullwidth}
    


        \titleBox{
            \textcolor{white}{\LARGE{\textbf{DIME Analytics \\ Peer Code Review - Analysis Checklist}} \\[5pt]}
        }
% Restore default margins after the first page


        \section*{Reviewer Details}
        \dimeTextField{reviewer}{6cm}{Reviewer Name:}  
        \dimeTextField{coder}{6cm}{ Coder Name:}  

        \vspace{0.5cm}

        \textbf{Note:} Please complete this checklist \textbf{only if} the submission includes \textbf{analysis} tasks.		
\section*{Analysis Tasks}
This checklist highlights key aspects to review in your partner's \textbf{analysis} scripts/code.  
Once completed, please submit it as an attachment along with \href{https://survey.wb.surveycto.com/collect/code_review_summary?caseid=}{this form}.

\subsection*{General Code Structure}
\begin{itemize}
    \setlength\itemsep{-0.1em}
    \item[] \dimeCheckBox{Analysis scripts do not create new variables, except when necessary for specific outputs (e.g., temporary transformations).}
    \item[] \dimeCheckBox{The code is modular, allowing individual outputs to be run in any order without dependencies on prior scripts.}
    \item[] \dimeCheckBox{All research decisions are well documented (e.g., including sample selection, missing data handling, etc.}
    \item[] \dimeCheckBox{The functions and statistical methods used are appropriate for the analysis being performed.}
    \item[] \dimeCheckBox{Categorical variables are used correctly (e.g., labeled integers are not mistakenly treated as continuous variables).}
\end{itemize}


\subsection*{Output Checks}
\begin{itemize}
    \setlength\itemsep{-0.1em}
    \item[] \dimeCheckBox{The code generates outputs as expected without errors or missing components.}
    \item[] \dimeCheckBox{Outputs (tables, figures, datasets) are exported in a reproducible manner, with minimal manual formatting.}
    \item[] \dimeCheckBox{Results are cross-checked with outputs shared for consistency (e.g., totals match across tables, key statistics align with expectations).}
\end{itemize}


    
            
		\vspace{.6em}


	\end{fullwidth}
\end{document}
