
\documentclass{tufte-handout}
\input{checklist-header}


\begin{document}
\thispagestyle{firstpage}
    \begin{fullwidth}

        \titleBox{
            \textcolor{white}{\LARGE{\textbf{DIME Analytics \\ Code Review Package Checklist}}}
        }

        \section*{Overview}
The submission package for peer code review should include all components in the checklist below. Code review participants can provide either a link to the complete package (\textbf{OneDrive} or \textbf{GitHub}), or a zipped folder - along with information on programming language(s) involved, and approximate run time. Questions should be directed to \href{mailto:dimeanalytics@worldbank.org}{DIME Analytics}.

        \section*{Package Requirements}
        \begin{enumerate}
        \item \textbf{Code:}
        \begin{itemize}
            \item[] \dimeCheckBox{All scripts to be reviewed.}
            \item[] \dimeCheckBox{A \textbf{main script} that allows the reviewer to run all code after changing only the top-level directory.   }        \end{itemize}
          
          \item \textbf{Data:}  
          \begin{itemize}
            \item[] \dimeCheckBox{All de-identified data necessary to run the code.}
           \end{itemize}
           
           \item \textbf{README:}
           \begin{itemize}
            \item[] \dimeCheckBox{A \href{https://github.com/worldbank/wb-reproducible-research-repository/blob/main/resources/README_Template.md}{README file} containing:}
                \begin{itemize}
                    \item[] \dimeCheckBox{Software and version used.}
                    \item[] \dimeCheckBox{Approximate run time of the code.}
                    \item[] \dimeCheckBox{Purpose of each folder.}
                    \item[] \dimeCheckBox{High-level objective of the code (e.g., regression analysis, data visualization).}
                    \item[] \dimeCheckBox{Line(s) in the \textbf{main script} that should be changed to run the code on a different machine.}
                    \item[] \dimeCheckBox{Purpose of each script (if multiple scripts are used).}
                    \item[] \dimeCheckBox{Outputs produced (if part of the review).}
                    \item[] \dimeCheckBox{Mapping of outputs to scripts responsible for generating them.}
                    \item[] \dimeCheckBox{Any specific requests or guidance for the reviewer.}
                \end{itemize}
            \item[] \dimeTextField{master}{11cm}{README file path and name:}
        \end{itemize}

        \section*{Component-Specific Requirements}
        Before submitting your package, ensure the following requirements are met.

        \subsection{1. \, Main Script Requirements}
        The main script should be structured to ensure smooth execution. See templates for \href{https://github.com/worldbank/wb-reproducible-research-repository/blob/main/resources/main.do}{Stata} and \href{https://github.com/worldbank/wb-reproducible-research-repository/blob/main/resources/main.R}{R} main scripts. 

        
        \begin{itemize}
            \item[] \dimeCheckBox{The main script runs from start to end after changing only directory paths in one location. This should be clearly specified in the README.}
            \item[] \dimeCheckBox{The main script installs any required packages or provides instructions to do so (e.g., SSC for Stata, CRAN for R).  Refer to this session on \href{https://osf.io/q7rjt}{Building Reproducible Environments} for more information.}
            \item[] \dimeCheckBox{For Stata, the main do-file sets critical configurations such as \texttt{version}, \texttt{matsize}, and \texttt{varabbrev}, either directly or via a wrapper command (e.g., \texttt{ieboilstart} from \texttt{ietoolkit}).}
            \item[] \dimeCheckBox{For R, all necessary packages are loaded within the main script.}
            \item[] \dimeTextField{time}{2.5cm}{\textbf{Approximate run time} of the main script:}
        \end{itemize}

        \subsection{2. \, Data Requirements}
        \begin{itemize}
            \item[] \dimeCheckBox{The data can be shared for the review.}
            \item[] \dimeCheckBox{The data is de-identified.}
            \item[] \dimeCheckBox{All necessary datasets are included in the package.}
        \end{itemize}

        \subsection{3. \, Output Requirements}
        \href{https://osf.io/ezmsb}{Refer to this session on Creating Reproducible Outputs for details.}

        \begin{itemize}
            \item[] \dimeCheckBox{All outputs generated by the code are included in the package.}
            \item[] \dimeCheckBox{Outputs are saved and stored in the appropriate folders (e.g., final outputs in \texttt{\textbf{Outputs/Final}}).}
        \end{itemize}

    \end{fullwidth}
\end{document}
