\input{checklist-header.tex}

% ------------------------------ End of preamble ---------------------------------------------
\begin{document}
	\begin{fullwidth}

\titleBox{
	\textcolor{white}{\LARGE{\textbf{DIME Analytics \\ Reproducibility Package Checklist}} \\
	\Large\textbf{{v1.4}}}
}

	\section*{Required Content and Practices}

	The reproducibility package must be shared as a .zip file, GitHub link or shared folder containing the items listed below.
	
	\subsection{1. \, Files}
	
	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeCheckBox{A filled version of this checklist.}
		\item[] \dimeCheckBox{A README file describing the folders and datasets included in the package, and any general or ad-hoc instructions about the directory structure or for the code to run.}
		\item[] \dimeCheckBox{A PDF version of the research output being reviewed (paper, brief, report).}
	\end{itemize}

	\subsection{2. \, Code}

	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeTextField{software}{8cm}{Software used (including version):}
		\item[] \dimeTextField{os}{8cm}{Operating system used:}
		\item[] \dimeCheckBox{All scripts needed to reproduce the analysis is included in the reproducibility package.}
		\item[] \dimeCheckBox{The reproducibility package includes a \textbf{master script}.}
		\item[] \dimeTextField{master}{11cm}{Master script path and name:}
	\end{itemize}

	\vspace{.6em}
	\noindent The items below only apply if the reproducibility package includes a master script.

	\begin{itemize}
		\setlength\itemsep{-0.1em}
		
		\item[] \dimeTextField{time}{2.5cm}{\textbf{Approximate time} it takes to recreate all results from the the master script: }
		\item[] \dimeTextField{ram}{2.5cm}{RAM size of computer used to calculate time:}

		\item[] \dimeCheckBox{The master script re-creates all raw outputs (e.g. tables and figures) when executed.}

		\item[] \dimeCheckBox{All raw outputs are re-created \textbf{as they appear in the paper}, requiring no manual changes.}

		\item[] \dimeCheckBox{All raw outputs are re-created in the same folder structure as they were submitted in the reproducibility package.}

		\item[] \dimeCheckBox{The master script \textbf{installs any commands required} (e.g. from SSC in Stata, CRAN in R, etc.).}

		\item[] \dimeCheckBox{In Stata, the master do file sets \textbf{critical configurations} such as \texttt{version}, \texttt{matsize}, and \texttt{varabbrev} (either sets directly or through a wrapper command such as \texttt{ieboilstart} from \texttt{ietoolkit}).}

		\item[] \dimeCheckBox{In R, all necessary packages to run the code are loaded in the master script.}
		\item[] \dimeCheckBox{All file paths in the code use only forward slashes, i.e. \texttt{C:/users/...}.}

		\vspace{0.3em}
		\item[] Select only one of the following two options.
		\vspace{-0.3em}
		\begin{itemize}
			\setlength\itemsep{-0.1em}
			\item[] \dimeCheckBox{Results are reproducible using the \textbf{most recent version} of the user-written commands (as available in CRAN/SSC) at the time of submitting the reproducibility package.}

			\item[] \dimeCheckBox{The master script installs the \textbf{exact version} of each package required, either from within the reproducibility package itself, or from a remote location.}
		\end{itemize}
	\end{itemize}

	\subsection{3. \, Data}

	The reproducibility package includes:
	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeCheckBox{Fully de-identified data. \textbf{Any exception where DIME Analytics needs to access restricted or sensitive data sets will require additional ethics and security measures, and will be handled on a case-by-case basis.}}

		\item[] \dimeCheckBox{All data necessary to run the master script that reproduces the analysis.}
	\end{itemize}

	\noindent Indicate the stage of the data this package begins reproducibility from (select only one):
	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeCheckBox{Raw data}
		\item[] \dimeCheckBox{Cleaned data}
		\item[] \dimeCheckBox{Cleaned data with constructed variables}
	\end{itemize}

	\noindent Indicate if the data or metadata used in this project or reproducibility package has been published:
	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeCheckBox{Yes, it has been published}
		\item[] \dimeCheckBox{No, it has not been published}
	\end{itemize}

	\noindent If it has been published, please indicate the URL or DOI of the data publication:
	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeTextField{data_url1}{13cm}{URL / DOI 1:}
		\item[] \dimeTextField{data_url2}{13cm}{URL / DOI 2:}
		\item[] \dimeTextField{data_url3}{13cm}{URL / DOI 3:}
	\end{itemize}



	\subsection{4. \, Outputs}

	The reproducibility package includes:

	\begin{itemize}
		\setlength\itemsep{-0.1em}
		\item[] \dimeCheckBox{All raw outputs used for the paper (e.g. tables and figures), as created by the code.}

		\item[] \dimeCheckBox{Files that clearly correspond by name to an exhibit in the paper, and vice versa.}
	\end{itemize}

	\noindent The items below may be left blank if they don't apply to the outputs in the package:
	\begin{itemize}
		\item[] \dimeCheckBox{If any formatting to a particular output is needed after running the code that creates it, all additional steps needed to create this output \textbf{as it appears in the paper} are indicated in the \textbf{master script} or a \textbf{readme} file. (DIME Analytics recommends against this practice.)}

		\item[] \dimeCheckBox{If any tables or figures included in the paper are not created through code (for example, a table with variable definitions), this is indicated in a \textbf{readme}.}
	\end{itemize}

	\newpage
	\section*{Access to Data and Documentation (recommended)}

		\begin{itemize}
			\setlength\itemsep{0.2em}
			\item[] \textbf{Code repository}
			\item[] \dimeTextField{code}{10cm}{URL:} \hspace{.3cm} \dimeCheckBox{Code repository is public}
			\vspace{0.2em}
			\item[] \textbf{Study registration}
			\item[] \dimeTextField{prereg}{10cm}{URL:} \hspace{.3cm} \dimeCheckBox{Study registration is public}
			\item[] \textbf{Pre-analysis plan}
			\item[] \dimeTextField{pap}{10cm}{URL:} \hspace{.3cm} \dimeCheckBox{Pre-analysis plan is public}
			\vspace{0.2em}
			\item[] \dimeTextField{other1}{7.7cm}{\textbf{Other document:}}
			\item[] \dimeTextField{other1url}{10cm}{URL:} \hspace{.3cm} \dimeCheckBox{Document is public}
			\vspace{0.2em}
			\item[] \dimeTextField{other2}{7.7cm}{\textbf{Other document:}}
			\item[] \dimeTextField{other2url}{10cm}{URL:} \hspace{.3cm} \dimeCheckBox{Document is public }
		\end{itemize}

	\newpage
	\section*{Recommended Practices}

		These practices are recommended but not required:
		\vspace{.3cm}

		\noindent \dimeCheckBox{The package includes all the necessary files to recreate the final analysis data set from the raw data (e.g., scripts for data cleaning and indicators construction are also provided).}

		\noindent \dimeCheckBox{Scripts for data cleaning, variable creation, and analysis are separate; and analysis scripts do not include any data processing, unless necessary for the creation of a table or graphic.}

		\noindent \dimeCheckBox{Variable construction scripts include detailed comments about each variable created.}

		\noindent \dimeCheckBox{Analysis scripts do not depend on having the results of other scripts in memory, except for the Master script.}

		\noindent \dimeCheckBox{Separate scripts are provided for each exhibit.}

		\noindent \dimeCheckBox{All scripts are well-commented and formatted, such that one can easily identify functional chunks of code and evaluate whether they correctly implement the econometric or statistical process described.}

		\noindent \dimeCheckBox{Graphics are output as \texttt{.eps} files or other vector images when possible.}

		\noindent \dimeCheckBox{Tables are output as \texttt{.csv} or \texttt{.tex} files or other raw text files when possible.}

		\noindent \dimeCheckBox{The submission package includes code to create all in-text numerical citations that are not drawn directly from tables and figures.}

		\noindent \dimeCheckBox{In-text numerical citations (other than those drawn directly from tables and figures) are computed and recorded in a dynamic document format like \texttt{.ipynb}, \texttt{.stmd} using \texttt{markstat} in Stata, or \texttt{.Rmd} using R.}

	\end{fullwidth}
\end{document}
